A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-13 paper/ms.tex
update ms

%\suppressAffiliations
%\NewPageAfterKeywords
\input{authors.tex}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx38$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    Gaia EDR3 Catalog of Nearby Stars (gray background;
    log-stretch).  The right panel is a zoomed view of 
    the pre-main-sequence.  The \cn\ and IC\,2602 are approximately
    the same isochronal age.  {\it Bottom:} TESS and Kepler stellar
    rotation periods versus dereddened Gaia colors, with the Pleiades
    and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most of the
    candidate \cn\ members are gyrochronally younger than the
    Pleiades.
   \label{fig:age}
	}
\end{figure*}

@@

\subsection{Color-Magnitude Diagram}
\label{sec:cmd}

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-magnitude diagram (CMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The
candidate \cn\ members shown are
selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical method
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and manually excluded stars that
were obvious photometric binaries in the CMD.  We then passed a moving
box average and standard deviation across the CMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.
The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.

Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
noted in the literature.

@@

To summarize, the age of the \cn\ cluster based on the empirical
pre-main-sequence interpolation is \clusterage.  This procedure hinges
on the age adopted for IC\,2602, since it is the closest reference
cluster in the color-magnitude diagram.  Gyrochronologically, while
most of the G and K dwarfs in the \cn\ have not yet converged to a
slow sequence, their rotation periods and those of the F dwarfs are
also consistent with a 30 to 50\,Myr age. The most precise age for
\sn\ and its planet are therefore also \clusterage\ Myr, based on the
star's spatial, kinematic, and rotational connection to the cluster,
and the assumption that the planet formed very quickly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet
\citep[see {\it e.g.},][]{soderblom_ages_2014}.
We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr ({\it e.g.}, 
\citealt{randich_gaiaeso_2018}; \citealt{bouma_2021_ngc2516}).

@@

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As discussed in Appendix~\ref{app:companionstar},
we discovered a low-mass stellar companion ($M_{\rm B}\approx
0.44\,M_\odot$), and so we reconsidered this false positive scenario
in some detail.

@@

We identified three new lines of evidence that support the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is
$\approx 3.2\,{\rm g\,cm}^{-3}$ (Table~\ref{tab:posterior};
\citealt{choi_mesa_2016}).  The transit duration is therefore too long
to explained by a star eclipsing the M dwarf secondary at
$\approx$$5$-$\sigma$.

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the
144 observed transits to within $\pm4.5$\,hr of each transit, and
fitted each window with both {\it i)} a local second-order polynomial
and transit, and {\it ii)} a local linear trend.  We let the mid-time
of each transit float, and then calculated the residual between the
measured mid-time and that of a perfectly periodic orbit.  This
residual, the transit timing variation (TTV), is plotted in
Figure~\ref{fig:obliquity} against the local linear slope.  A
significant correlation of $-0.0564 \pm 0.0098\ {\rm ppt\,day}^{-1}$
is observed.  Less than ten Kepler Objects of Interest have shown this
correlation \citep{holczer_time_2015}, which is most readily
interpreted as a TTV induced by unresolved starspot crossings
\citep{mazeh_time_2015}.  This is only possible if the planet transits
the primary star, which excludes a background eclipsing binary
scenario, and therefore confirms that \pn\ is a planet.  It also
implies that the planet's orbit is prograde.  The latter
interpretation assumes that the dominant photometric variability is
induced by dark spots, rather than bright faculae
\citep{mazeh_time_2015}.  Given the observed transition of Sun-like
stellar variability from spot to faculae-dominated regimes, we expect
this inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 7 Aug 2021 (UT).  We
used the iodine cell for the wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term is included.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.  More data will be needed however to
make a more precise measurement of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of Doppler transits could yield a more precise stellar
obliquity, and could confirm or refute the expected prograde orbital
geometry.  Similarly, transit spectroscopy aimed at detecting outflows
of hydrogen or helium could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{spake_helium_2018,vissapragada_2020}.  Determining the
precise level of high-energy irradiation incident on the planet would
also help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, perhaps the most challenging,
but also the most informative measurement would be to determine the
planet's mass.  This might be possible either through detailed timing
analyses of the Kepler data, or through a high-cadence multi-color
radial velocity campaign.  Measured at sufficient precision, the mass
could yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
clearly significant planet-planet TTVs, the star's flaring may be
suggestive of star-planet interactions.  Appendix~\ref{app:flare}
highlights an odd flare timing coincidence that may be worthy of
further examination.

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities would be in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties consistent
with a quiescent disk-driven migration history.  The alternative
scenario of in-situ formation is disfavored on theoretical grounds:
the required disk mass would likely drive migration, and so lacks
internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   The age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from the TESS mission
\citep{ricker_transiting_2015,guerrero_tess_2021}.  An alternative
path toward age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancilliary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes
stars that are young, age-dated, and age-dateable.  By ``age-dateable'',
we mean that the age should be measurable at greater
precision than a typical FGK field star.
As in
\citet{bouma_cdipsI_2019}, we collected stars that met these criteria
from across the literature.  Table~\ref{tab:metadata} gives a list of
the studies included, and some brief summary statistics.
The age measurement approaches adopted by each study differ: in many,
spatial and kinematic clustering has been performed on the Gaia data,
and ensemble isochrone fitting of the cluster has been performed
(typically focusing on the turn-off).
In others however, the claim of youth is based on the location of a
single star in the color-magnitude diagram, or on spectroscopic
information.

>>>>

%\suppressAffiliations
\NewPageAfterKeywords
\input{authors.tex}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-absolute magnitude diagram of candidate \cn\ members, in addition to
    stars in IC\,2602 ($\approx38$\,Myr), the Pleiades ($\approx
    115$\,Myr; \citealt{dahm_2015}), and the Gaia EDR3 Catalog of
    Nearby Stars (gray background).  The right panel is a
    zoomed view of the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation periods versus dereddened Gaia colors,
    with the Pleiades and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  Most
    candidate \cn\ members are gyrochronally younger than the
    Pleiades; outliers are probably field interlopers.
   \label{fig:age}
	}
\end{figure*}

@@

\subsection{Color-Absolute Magnitude Diagram}
\label{sec:camd}

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-absolute magnitude
diagram (CAMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The
candidate \cn\ members shown are
selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical method
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and manually excluded stars that
were obvious photometric binaries in the CAMD.  We then passed a moving
box average and standard deviation across the CAMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CAMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.
The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}. 
Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
noted in the literature.

@@

In summary, the age of the \cn\ cluster based on the empirical
pre-main-sequence interpolation method is \clusterage.  This method
hinges on the age adopted for IC\,2602, since it is the closest
reference cluster in the color-absolute magnitude diagram.
Gyrochronologically, while most of the FGK dwarfs in the \cn\ have
not yet converged to a slow sequence, their rotation periods 
are generally consistent with an $\approx$38\,Myr age. The most
precise age for \sn\ and its planet are therefore identical to the cluster,
based on the star's spatial and kinematic association with the
cluster, and the assumption that the planet formed shortly after
the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet \citep[see {\it
e.g.},][]{soderblom_ages_2014}.  We acquired an iodine-free spectrum
from Keck/HIRES on the night of 26 March 2021 using the standard setup
and reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the
effective temperature of \sn\ (Table~\ref{tab:starparams}), this
measurement is also in line with expectations for a $\approx$38\,Myr
star ({\it e.g.}, \citealt{randich_gaiaeso_2018};
\citealt{bouma_2021_ngc2516}).

@@

Could the transit signal be produced by anything other than a planet
orbiting this near-solar analog?  \citet{morton_false_2016} validated
the planet based on the transit shape, arguing that the most probable 
false positive scenario was that of a background eclipsing binary,
which had a model-dependent probability of $\approx10^{-5}$.
As we describe in Appendix~\ref{app:companionstar} however,
the system has a low-mass stellar companion ($M_{\rm B}\approx
0.44\,M_\odot$), and so we reconsidered this false positive scenario
in some detail.

@@

There are three new lines of evidence that support the planetary
interpretation.  First, the transit duration and the orbital period
are inconsistent with an eclipsing body around the M-dwarf companion:
we find $\rho_\star = 2.00 \pm 0.24\,{\rm g\,cm}^{-3}$, while the
theoretically expected density for the companion is
$\approx 3.2\,{\rm g\,cm}^{-3}$ (Table~\ref{tab:posterior};
\citealt{choi_mesa_2016}).  The transit duration is therefore too long
to be explained by a star eclipsing the M dwarf secondary at
$\approx$$5$-$\sigma$.

@@

The second line of confirmatory evidence comes by analyzing the
individual Kepler transit times. We isolated each of the
144 observed transits to within $\pm4.5$\,hr of each transit, and
fitted each window with both {\it i)} a local second-order polynomial
and transit, and {\it ii)} a local linear trend.  We let the mid-time
of each transit float, and then calculated the residual between the
measured mid-time and that of a periodic orbit.  This
residual, the transit timing variation (TTV), is plotted in
Figure~\ref{fig:obliquity} against the local linear slope.  A
significant correlation of $-0.0564 \pm 0.0098\ {\rm ppt\,day}^{-1}$
is observed.  Less than ten Kepler Objects of Interest have shown this
correlation \citep{holczer_time_2015}, which is most readily
interpreted as a TTV induced by unresolved starspot crossings
\citep{mazeh_time_2015}.  This is only possible if the planet transits
the primary star, which excludes a background eclipsing binary
scenario, and therefore confirms that \pn\ is a planet.  It also
implies that the planet's orbit is prograde.  The latter
interpretation assumes that the dominant photometric variability is
induced by dark spots, rather than bright faculae
\citep{mazeh_time_2015}.  Given the observed transition of Sun-like
stellar variability from spot to faculae-dominated regimes, we expect
this inference to be reasonably secure
\citep{shapiro_are_2016,montet_long-term_2017,reinhold_stellar_2020}.

The final piece of evidence comes from a spectroscopic transit we
observed using Keck/HIRES during the night of 7 Aug 2021.  We
used the iodine cell for the wavelength calibration, and scheduled the
transit using the ephemeris of \citet{holczer_transit_2016}.  We also acquired
simultaneous multi-band photometry using MuSCAT3 \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, and an
increase in RV is seen shortly after the expected ingress time.  The
internal uncertainty on the RVs ($\approx 15\,{\rm m\,s}^{-1}$) is
dominated by the $v\sin i$ broadening.

@@

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed the
sky-projected obliquity, the stellar equatorial velocity, and the
Gaussian dispersion of the spectral lines to vary.  We also allowed
for an optional linear and quadratic trend, and a white-noise jitter
term.  The quadratic model with the RM effect is shown in
Figure~\ref{fig:obliquity}; the prior on $v\sin i$ has been assumed
from Table~\ref{tab:starparams}, and the jitter term has been
incorpoarted.
We found $\chi^2_{\rm red} =
5.4$ for the best-fitting linear case, and $\chi^2_{\rm red} = 4.4$
for the best-fitting quadratic, with a $\Delta {\rm BIC} = {\rm
BIC}_{\rm line} - {\rm BIC}_{\rm quad} = 19.6$ and $\Delta {\rm AIC} =
{\rm AIC}_{\rm line} - {\rm AIC}_{\rm quad} = 20.6$.  While this
provides strong statistical evidence to prefer the quadratic model
over the linear one, the $\chi^2_{\rm red}$ indicate that neither fit
is very good.  Considering a quadratic trend without any RM
effect yields $\chi^2_{\rm red} = 4.3$, and $\Delta {\rm BIC} = {\rm
BIC}_{\rm trend} - {\rm BIC}_{\rm quad} = 1.9$ ($\Delta {\rm
AIC}=5.2$).  From a model-comparison standpoint, there is therefore
only marginal statistical evidence to prefer the best-fitting ``RM and
quadratic trend'' model over the best-fitting ``quadratic trend only''
model.  Given the expected semi-amplitude of the velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$) and the achieved precision,
we cannot claim a detection of the Doppler transit.
From the MuSCAT3 data however, we do know that the transit
was observed, and the increase in radial velocity seen shortly after
ingress is more consistent with a prograde or polar orbit than a
retrograde orbit.  Fixing the orbit to be either exactly prograde or
exactly retrograde, we find $\Delta {\rm BIC} = {\rm BIC}_{\rm
retrograde} - {\rm BIC}_{\rm trend} = 18.0$; the retrograde case is
ruled out on this basis.
% More data will be needed however to
% make a more precise measurement of the stellar obliquity.

@@

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Further
observations of Doppler transits could yield a more precise stellar
obliquity, and could confirm or refute the expected prograde orbital
geometry.  Similarly, transit spectroscopy aimed at detecting outflows
of hydrogen or helium could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{spake_helium_2018,vissapragada_2020}.  Determining the
precise amount of high-energy irradiation incident on the planet would
also help in clarifying the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  This might be
possible either through detailed timing analyses of the Kepler data,
or through a high-cadence multi-color radial velocity campaign.
Measured at sufficient precision, the mass could yield constraints on
both the planet's composition and its initial entropy
\citep{owen_constraining_2020}.

Separately, the Kepler data may yet contain further information.
Although our transit timing study did not yield the detection of any
clearly significant planet-planet TTVs, Appendix~\ref{app:flare}
highlights an odd flare timing coincidence that may be suggestive of
star-planet interactions.  We mention it here to encourage its
exploration by investigators more versed in the topic than ourselves.

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($3.34\pm
0.18\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities would be in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties consistent
with a quiescent disk-driven migration history.  The alternative
scenario of in-situ formation is disfavored on theoretical grounds:
the required disk mass would likely drive migration, and so lacks
internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work is a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.
Table~\ref{tab:v06} should enable similar cross-matches to already
known planets, as well as forthcoming planets from the TESS mission
\citep{ricker_transiting_2015,guerrero_tess_2021}.  An alternative
path toward age-dating more planets could be to identify kinematic
associations around known exoplanet host stars using positions and
tangential velocities from Gaia, and to then verify these associations
with ancillary rotation periods and spectroscopy \citep[{\it
e.g.},][]{tofflemire_tess_2021}.

@@

The \texttt{v0.6} CDIPS target catalog (Table~\ref{tab:v06}) includes
stars that are young, age-dated, and age-dateable.  By ``age-dateable'',
we mean that the age should be measurable at greater
precision than a typical FGK field star.
As in
\citet{bouma_cdipsI_2019}, we collected stars that met these criteria
from across the literature.  Table~\ref{tab:metadata} gives a list of
the studies included, and brief summary statistics.
The age measurement methodologies adopted by each study differ: in many,
spatial and kinematic clustering has been performed on the Gaia data,
and ensemble isochrone fitting of the resulting clusters has been performed
(typically focusing on the turn-off).
In other studies however, the claim of youth is based on the location of a
single star in the color-absolute magnitude diagram, or on spectroscopic
information.
